\mytitle

### 2020-04-09 paper.tex
minor in evaluation.

@@

\paragraph{Experimental Setting and Implementation Details}

>>>>

In this section, we 
present an empirical evaluation of our quadratic models based on 
standard WFLO instances.
Our main results are: \begin{itemize}
	\item QUBO based WFLO using the digital annealer provides state-of-the-art results in seconds.
	\item Given enough time LS quadratic models are superior to both linear models and to an SS approximations. 
\end{itemize}
We start by outlining the experimental design of our evaluation, followed by a presentation of our main results
and a discussion of the results together with the limitations of the approach.

@@

\paragraph{Experimental Setting}

\paragraph{Implementation Details}
